pipeComp, a general framework for the evaluation of computational pipelines, reveals performant single cell RNA-seq preprocessing tools

### 2020-05-08 bmc_article.tex

\begin{table}[h!]
\caption{Overview of the benchmark datasets.}
\label{tab:table1}
\begin{tabular}{rlrrl}
  \hline
dataset & source & \# cells & protocol & description \\ 
  \hline
Koh & GSE85066 & 531 & SMARTer & FACS purified differentiation stages \\ 
  Kumar & GSE60749 & 246 & SMARTer & Mouse ESC cultured in different conditions \\ 
  Zhengmix4eq & \cite{duoClustering2018} & 3994 & 10x & Mixtures of FACS purified PBMCs \\ 
  Zhengmix4uneq & \cite{duoClustering2018} & 6498 & 10x & Mixtures of FACS purified PBMCs \\ 
  Zhengmix8eq & \cite{duoClustering2018} & 3994 & 10x & Mixtures of FACS purified PBMCs \\ 
  mixology10x3cl & \cite{tianMixology2018} & 902 & 10x & Mixture of 3  cancer cell lines from CellBench \\ 
  mixology10x5cl & \cite{tianMixology2018} & 3918 & 10x & Mixture of 5 cancer cell lines from CellBench \\ 
  simMix1 & - & 2500 & 10x-based & Simulation of 10 human cell subpopulations \\
  simMix2 & - & 3000 & 10x-based & Simulation of 9 mouse cell subpopulations \\
   \hline
\end{tabular}
\end{table}

@@

\section*{Additional Files}
  \subsection*{\textbf{Additional file 1: Supplementary figures}}
  Additional results of evaluations across datasets among various metrics. (PDF 15 MB)
  \subsection*{\textbf{Additional file 2: Supplementary methods}}
  More detailed description of \textit{pipeComp} and comparison with other tools. (PDF 0.5 MB)
\end{backmatter}
\end{document}

>>>>

\begin{table}[h!]
\caption{\textbf{Overview of the benchmark datasets.} `\# features' indicates the number of features detected in at least 10 cells.}
\label{tab:table1}
\begin{tabular}{rlrrl}
  \hline
dataset & \# features & \# cells & protocol & description \\ 
  \hline
Koh & 33922 & 531 & SMARTer & FACS purified differentiation stages \\ 
  Kumar & 41930 & 246 & SMARTer & Mouse ESC cultured in different conditions \\ 
  Zhengmix4eq & 10434 & 3994 & 10x & Mixtures of FACS purified PBMCs \\ 
  Zhengmix4uneq & 11369 & 6498 & 10x & Mixtures of FACS purified PBMCs \\ 
  Zhengmix8eq & 10600 & 3994 & 10x & Mixtures of FACS purified PBMCs \\ 
  mixology10x3cl & 16208 & 902 & 10x & Mixture of 3  cancer cell lines from CellBench \\ 
  mixology10x5cl & 11786 & 3918 & 10x & Mixture of 5 cancer cell lines from CellBench \\ 
  simMix1 & 3696 & 2500 & 10x-based & Simulation of 10 human cell subpopulations \\
  simMix2 & 8893 & 3000 & 10x-based & Simulation of 9 mouse cell subpopulations \\
   \hline
\end{tabular}
\end{table}

@@

\section*{Additional Files}
  \subsection*{\textbf{Additional file 1: Supplementary figures}}
  Additional results of evaluations across datasets among various metrics. (PDF 16 MB)
  \subsection*{\textbf{Additional file 2: Supplementary methods}}
  More detailed description of \textit{pipeComp} and comparison with other tools. (PDF 0.5 MB)
\end{backmatter}
\end{document}
